Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-06 paper/ms.tex
oops order
Add smoh orcid id
Fix typo
Edit abstract grammar etc.

\author{Semyeong Oh} % TODO: need ORCID
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars are separated $0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-resolution radial velocity measurements.
  Their stellar parameters determined from high-resolution KECK spectra
  indicate that both stars are $\sim 4$~Gyr old,
  yet both stars show high surface \elem{Li} abundance considering their ages.
  Moreoever, the more metal-rich of the two, HD~240430, shows an enhancement of
  refractory ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as
  large enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}):
  this is the largest and the most significant difference found in
  wide binary pairs yet.
  The proximity in phase space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  In order to reconcile the seemingly contradictory observations, we suggest
  that the star recently accreted $\approx 20$~\mearth\ of rocky material after
  birth selectively enhancing the refractory elements in its surface and
  convective envelope.
  The other star, HD~240429, may also have had a similar accretion event given
  its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  Follow-ups to study the existence and properties of the planetary systems
  around these stars will help illuminate more on planet-star interactions.
\end{abstract}

@@

Here, we report and discuss the discovery of a comoving pair of solar twin stars,
HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
We nickname the two stars \bizarreone\ (HD~240430) and
\sunanalog\ (HD~240429) throughout the \documentname.
In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
about the two stars relevant to the present discussion.
In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
the abundance difference between the pair.
We summarize or discussions in \sectionname~\ref{sec:summary}.

>>>>

\author[0000-0001-7790-5308]{Semyeong Oh}
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-resolution radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old,
  yet both stars show high surface \elem{Li} abundance for this age.
  The more metal-rich of the two, HD~240430, shows an enhancement of
  refractory ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as
  large enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}):
  this is the largest and the most significant difference found in
  wide binary pairs yet.
  The proximity in phase space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted $\approx 20$~\mearth\ of
  rocky material after birth selectively enhancing the refractory elements in
  its surface and convective envelope.
  The other star HD~240429, ``Krios'', may also have had a similar accretion event given
  its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  Follow-ups to study the existence and properties of the planetary systems
  around these stars will help illuminate more on planet-star interactions.
\end{abstract}

@@

Here, we report and discuss the discovery of a comoving pair of solar twin stars,
HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
We nickname the two stars \bizarreone\ (HD~240430) and
\sunanalog\ (HD~240429) throughout the \documentname.
In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
about the two stars relevant to the present discussion.
In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
the abundance difference between the pair.
We summarize our discussions in \sectionname~\ref{sec:summary}.
